Trends of SDR in Thessaloniki

### 2023-06-07 Article.Rmd
Commit 2023-06-07 16:17

output: 
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:  article
    classoption:    a4paper,oneside
    fontsize:       12pt
# geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
# link-citations: yes
# colorlinks:     yes
# urlcolor:       blue
# bibliography:   [references.bib]
# biblio-style:   apalike
# date:           "`r format(Sys.time(), '%F')`"
---

>>>>

output: 
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:  article
    classoption:    a4paper,oneside
    fontsize:       12pt
    geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
    link-citations: yes
    colorlinks:     yes
    urlcolor:       blue
    biblio-style:   apalike
# date:           "`r format(Sys.time(), '%F')`"
---
